Grocery Pricing Strategies: An Analysis of Vendor Positioning and Market Dynamics

### 2024-11-14 paper/paper.qmd
update paper

---
title: "Grocery Pricing Strategies: An Analysis of Vendor Positioning and Market Dynamics"
subtitle: "Examining Sales Frequency, Price Distribution, and Average Price Levels Across Major Grocery Chains"
author: 
  - Andy Jiang
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/grocery-price-analysis.git)."
date: today
date-format: long
abstract: "This paper examines grocery pricing strategies across major vendors to understand how they position themselves in a competitive market. By analyzing sales frequency, price distribution, and average price levels, we identify distinct approaches used by each vendor to attract customers. Our findings reveal that some vendors, like Metro, rely on frequent promotions to appeal to a broad customer base, while others, such as No Frills and Walmart, prioritize everyday low pricing to cater to budget-conscious shoppers. This analysis highlights the varied tactics grocery vendors use to target different consumer segments, providing insights into the competitive dynamics that shape grocery pricing and customer choices."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

>>>>

---
title: "Grocery Pricing Strategies: An Analysis of Vendor Positioning and Market Dynamics"
subtitle: "Examining Sales Frequency, Price Distribution, and Average Price Levels Across Major Grocery Chains"
author: 
  - Andy Jiang
  - Rui Hu
  - Onon Burentuvshin
thanks: "Code and data are available at: [https://github.com/AndyYanxunJiang/grocery-price-analysis.git)."
date: today
date-format: long
abstract: "This paper examines grocery pricing strategies across major vendors to understand how they position themselves in a competitive market. By analyzing sales frequency, price distribution, and average price levels, we identify distinct approaches used by each vendor to attract customers. Our findings reveal that some vendors, like Metro, rely on frequent promotions to appeal to a broad customer base, while others, such as No Frills and Walmart, prioritize everyday low pricing to cater to budget-conscious shoppers. This analysis highlights the varied tactics grocery vendors use to target different consumer segments, providing insights into the competitive dynamics that shape grocery pricing and customer choices."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---
